Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-07 Ben_Manuscripts/transport/Draft.tex
Add missing files

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  %MRS3:
  candidates
  for selective separation membranes. 
  %MRS3: I do worry that the above makes it look like we are not acknowledging the formulation problems.  Maybe something like: 
  %''models of how chemically selective separation membranes could can function''?  So the focus is more on the science that these membranes could reveal, rather than saying they are good membranes now?  Then we talk about new membranes at the end of the introduction. Thoughts? I didn't go ahead and make  the change since it needs a bit more thought.  I'm open to other ways to reformulate.  Some of this thinking will percolate into the rest of the introduction as well.
  In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.~\cite{zhou_supported_2005}

@@

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. These membranes have been primarily characterized with 
  size-exclusion experiments which can give an estimate of pore size as well as
  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
  However, size exclusion does not appear to be sufficient to fully describe LLC
  membranes. Dischinger et al. studied a similar membrane and found that they do
  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
  between various solute physicochemical properties and observed solute rejection. 
  Although there was some agreement with their empirical model, it does not
  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}

%  The separation performance of these membranes has been 
%  primarily characterized with size-exclusion experiments which emphasizes 
%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
%  %separation BY size exclusion; maybe rephrase?
%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
%  While size-exclusion is a useful separation, it 
%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
%  important to take advantage of material properties other than pore size. 
%  Unfortunately, this is a more complicated design problem. Experimental transport
%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
%  unclear trends due to interactions between solutes and pore moieties. Although
%  the authors identified some correlation between select physicochemical properties
%  and solute transport trends, their empirical model does not offer a sufficient 
%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?

>>>>

  The uniform size and complex chemical topology of the pores that 
  constitute cross-linked inverted hexagonal (H\textsubscript{II})
  phase lyotropic liquid crystal (LLC) membranes make them promising
  candidates for selective separation membranes. 
  %MRS3: I do worry that the above makes it look like we are not acknowledging
  %the formulation problems.  Maybe something like: ''models of how chemically
  %selective separation membranes could can function''?  So the focus is more
  %on the science that these membranes could reveal, rather than saying they
  %are good membranes now?  Then we talk about new membranes at the end of the
  %introduction. Thoughts? I didn't go ahead and make  the change since it
  %needs a bit more thought.  I'm open to other ways to reformulate.  Some of
  %this thinking will percolate into the rest of the introduction as well.
  In this work, we observe transport
  of water, sodium ions and 20 small polar solutes within the pores 
  of an LLC membrane using atomistic molecular simulations. We 
  find that the transport of a species is dependent not only on 
  molecular size, but on chemical functionality as well. The 
  membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe
  that all solutes perform intermittent hops between lengthy
  periods of entrapment. Three different trapping mechanisms are 
  responsible for this behavior. First, solutes that drift
  out of the pore can become entangled among the dense monomer
  tails. Second, solutes can donate hydrogen bonds to the monomer
  head groups. Third, solutes can coordinate with sodium counter ions.
  The degree to which a solute is affected by each mechanism is 
  dependent on the chemical functionality of the solute. Using the
  insights developed in this study, we can begin to think about 
  how to redesign existing LLC membranes in order to perform 
  solute-specific separations.

@@

% re-outline from here.

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}

  Under the right conditions, amphiphilic molecules can self-assemble
  into ordered nanostructures that may be capable of performing highly selective separations.
  \begin{itemize}
    \item Uniform-sized pores characteristic of these systems enforce a 
    molecular-size cut-off, eliminating issues related to the polydisperity 
    of NF pores.
    \item By controlling the chemical identity of moeties inside the pores, 
    it may be possible to tune these types of materials for solute-specific
    separations.
  \end{itemize}

  Lyotropic liquid crystals (LLCs) are known to form the type I bicontinuous
  (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II}) phases.
  \begin{itemize}
	\item When cross-linked, these materials can function as separations
	 membranes.
	\item The H\textsubscript{II}
  \end{itemize}

%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.~\cite{zhou_supported_2005}

@@

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. These membranes have been primarily characterized with 
  size-exclusion experiments which can give an estimate of pore size as well as
  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
  However, size exclusion does not appear to be sufficient to fully describe LLC
  membranes. Dischinger et al. studied a similar membrane and found that they do
  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
  between various solute physicochemical properties and observed solute rejection. 
  Although there was some agreement with their empirical model, it does not
  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
%============= 
%  The separation performance of these membranes has been 
%  primarily characterized with size-exclusion experiments which emphasizes 
%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
%  %separation BY size exclusion; maybe rephrase?
%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
%  While size-exclusion is a useful separation, it 
%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
%  important to take advantage of material properties other than pore size. 
%  Unfortunately, this is a more complicated design problem. Experimental transport
%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
%  unclear trends due to interactions between solutes and pore moieties. Although
%  the authors identified some correlation between select physicochemical properties
%  and solute transport trends, their empirical model does not offer a sufficient 
%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
